Basketball: an analysis of a single game

### 2021-01-22 inst/NBA.Rmd
corrections

```{r,definsupportb,cache=TRUE}
allplayers <- as.matrix(NBA_table[,5:23])
NBA <- hyper2()

@@

for(i in seq_len(nrow(NBA_table))){
  if(scored[i] == 'W'){  # Warriors score a point
    onpitch_scored  <- names(which(W_onpitch[i,]))
    onpitch_noscore <- names(which(C_onpitch[i,]))
  } else if(scored[i] == "C"){ # Cleveland score a point
    onpitch_scored  <- names(which(C_onpitch[i,]))
    onpitch_noscore <- names(which(W_onpitch[i,]))
  } else {
    stop("scorint team must be either W or C")
  }
  if(possession[i] == 'W'){
    onpitch_scored <- c(onpitch_scored,"W_possession")
  } else if (possession[i] == 'C'){
    onpitch_scored <- c(onpitch_scored,"C_possession")
  } else {
    stop("possession must be either W or C")
  }
  NBA[onpitch_scored] %<>% inc()
  NBA[c(onpitch_scored,onpitch_noscore)] %<>% dec()
}

NBA_maxp <- maxp(NBA)
NBA_maxp %<>% ordertrans(c(colnames(NBA_table)[-(1:4)],"C_possession","W_possession"))
dotchart(NBA_maxp,col=c(rep("black",9),rep("red",10),rep("blue",2)),pch=16)
```

@@

```{r,statsanal,cache=TRUE}
samep.test(NBA,c("C_possession","W_possession"))
```

We may thus assume that Cleveland having possession is the same
strength as the Warriors having possession.

@@

```{r}
C_allstrengths <- sort(NBA_maxp[01:9],decreasing=TRUE)
W_allstrengths <- sort(NBA_maxp[10:19],decreasing=TRUE)
C_strongestteam <- sum(C_allstrengths[1:5])
W_strongestteam <- sum(W_allstrengths[1:5])
possession <- 0.2155786 # taken from samep.test() above

>>>>

```{r,definsupportb,cache=TRUE}
allplayers <- as.matrix(NBA_table[,5:23])
NBA <- hyper2()
NBA2 <- hyper2()

@@

for(i in seq_len(nrow(NBA_table))){
  if(scored[i] == 'W'){  # Warriors score a point
    onpitch_scored  <- names(which(W_onpitch[i,]))
    onpitch_noscore <- names(which(C_onpitch[i,]))
  } else if(scored[i] == "C"){ # Cleveland score a point
    onpitch_scored  <- names(which(C_onpitch[i,]))
    onpitch_noscore <- names(which(W_onpitch[i,]))
  } else {
    stop("scorint team must be either W or C")
  }
  print(onpitch_scored)
  print(onpitch_noscore)
  if(possession[i] == 'W'){
    onpitch_scored1 <- c(onpitch_scored,"possession")
    onpitch_scored2 <- c(onpitch_scored,"W_possession")
  } else if (possession[i] == 'C'){
    onpitch_scored1 <- c(onpitch_scored,"possession")
    onpitch_scored2 <- c(onpitch_scored,"C_possession")
  } else {
    stop("possession must be either W or C")
  }

  NBA[onpitch_scored1] %<>% inc()
  NBA[c(onpitch_scored1,onpitch_noscore)] %<>% dec()

  NBA2[onpitch_scored2] %<>% inc()
  NBA2[c(onpitch_scored,onpitch_noscore)] %<>% dec()
}

NBA2_maxp <- maxp(NBA2)
NBA2_maxp %<>% ordertrans(c(colnames(NBA_table)[-(1:4)],"C_possession","W_possession"))
dotchart(NBA2_maxp,col=c(rep("black",9),rep("red",10),rep("blue",2)),pch=16)

NBA_maxp <- maxp(NBA)
NBA_maxp %<>% ordertrans(c(colnames(NBA_table)[-(1:4)],"possession"))
dotchart(NBA_maxp,col=c(rep("black",9),rep("red",10),rep("blue",1)),pch=16)
```

@@

```{r,statsanal,cache=TRUE}
samep.test(NBA2,c("C_possession","W_possession"))
```

We may thus assume that Cleveland having possession is the same
strength as the Warriors having possession, and from now on we work
with `NBA` rather than `NBA2`.

```{r,cache=TRUE}
(C_allstrengths <- sort(NBA_maxp[01:9],decreasing=TRUE))
(W_allstrengths <- sort(NBA_maxp[10:19],decreasing=TRUE))
samep.test(NBA, names(C_allstrengths))
samep.test(NBA, names(W_allstrengths))
```

@@

```{r}
C_strongestteam <- sum(C_allstrengths[1:5])
W_strongestteam <- sum(W_allstrengths[1:5])
possession <- 0.2155786 # taken from samep.test() above
